My title

### 2024-11-26 paper/paper.qmd
setup basic structure for Data section & added content points to discussion

---
title: "My title"
subtitle: "Impact Analysis of Japanese Occupation on Population Shifts Across Shanghai’s Districts During WWII"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/Shanghai_population_change/tree/main"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Overview text

## Historical Background
- breifly introduces the necessary historical background for this analysis

@@

- how population is recorded (not accurate count but by householad then estimates by average)
- why use population density instead of pure population #

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

@@

Talk way more about it.

@@

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

@@

## Job Oppurtunities
Aside from the instability caused by the Japanese armed forces, there are a few other reasons for Chinese population to move into the international settlement & French Concession.
1. Job opportunities
- Heart of Shanghai city in the 1930-1940s, high pop density lead to boom of economy = more job opportunities
- many factories are located with the settlements (less so in concession)

## Barrier to Entry in Job Market
2. Barrier to Entry for certain job types
- 旧时候 -- 通讯还没有那么发达的时候，人们都很团结。那个时候同乡会的力量很强大。在外省，从同一个省来的漂泊者会互相帮扶着垄断一个城市的某种行业。例如，在旧上海，要做酒店生意的话你就必须是湖南人，给人做洗脚生意的肯定是苏北人。。。

>>>>

---
title: "My title"
subtitle: "Impact Analysis of Japanese Occupation on Population Shifts Across Shanghai’s Districts During WWII"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/Shanghai_population_change"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

## Data Sources
- talk about where the data in my primary reference book is gathered
- mentions the credibility of source and unstability of recording instrument & methodology

## Historical Background
Place: Shanghai, China
When: 1936-1942
Who: Chinese population in Shanghai

Define:
1. give 1-2 sentence broad overview of China's state of unrest
2.THREE districts in Shanghai: Chinese District, International Settlement, French Concession
- who controlled each district and the level of governance each authority have in comparison to Chinese government
3.Outline area (%) of each district (do not get into specifics, put that in Results section)

Important Event Timeline
1. 1937-08-13: Japanese armed forces entered Shanghai
2. 1937-11-12: Japanese armed forces claims occupation of Shanghai --> ends Chinese district 
3. 1942-01: Japanese armed forces claims authority over International Settlement (which was mainly under the governance of U.K and U.S prior to this date)
4. 1945-08-15: Japan surrendered in WWII
5. 1945-10: most Japanese armed forces withdrawed from Shanghai

@@

- how population is recorded (not accurate count but by householad then estimates by average)
- why use population density instead of pure population #
- how year variables correspond to the timeline (ex. if an event occured in Nov of 1937, would I take valeus of 1937 as a variable for prior to event occurance or after?)

## Outcome variables
- outcome variable is "population change in International Settlement during 1937-1942" measured in population density

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
Some of our data is of penguins (@fig-bills), from @palmerpenguins.

@@

@@

- most important predictors include time sensitive indicators: Event1 & Event2

Event1: indicator variable for 1937 (1 if year >= 1937 & <= 1941, 0 otherwise)
- mention a bit about the measurement

Event2: indicator variable for 1937 (1 if year >= 1941, 0 otherwise)
- mention a bit about the measurement

@@

### Job Oppurtunities in Shanghai
Aside from the instability caused by the Japanese armed forces, there are a few other reasons for Chinese population to move into the international settlement & French Concession.
1. Job opportunities
- Heart of Shanghai city in the 1930-1940s, high pop density lead to boom of economy = more job opportunities
- many factories are located with the settlements (less so in concession)

### Barrier to Entry in Job Market
2. Barrier to Entry for certain job types
- 旧时候 -- 通讯还没有那么发达的时候，人们都很团结。那个时候同乡会的力量很强大。在外省，从同一个省来的漂泊者会互相帮扶着垄断一个城市的某种行业。例如，在旧上海，要做酒店生意的话你就必须是湖南人，给人做洗脚生意的肯定是苏北人。。。

## Instability after Japanese Occupation ends in WWII: Chinese Civil War
- after the Japanese armed forces withdrawed from Shanghai, what follows is not recovery and rest for the local population
- Competition for power within China's 2 political parties caused full-scale political warfare, now known as the *Chinese Civil War*
- unlike Western political parties, Chinese political parties in the 1900s are more like parties of a throne. They each have their own ideology and an armed forces that follow. Most of all of the provinces are effected by this internal warfare, which ended in 1949 as 国民党 lost and withdrawed to Taiwan.
